---
title: "Modeling and prediction for movies"
output: md_document
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(statsr)
library(GGally)
library(gridExtra)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `movies`. Delete this note when before you submit 
your work. 

```{r load-data}
setwd("D:\\CourseraCourses\\StatisticsWithR\\Regression models\\Week4")
load("movies.Rdata")
head(movies)
```



* * *

## Part 1: Data

## Introduction : About data 
 Taken From IMBD, the data set is comprised of 651 randomly sampled movies produced and released before 2016. 


* * *

## Part 2: Research question

1. What's the best for predicting IMDB Rating ?

* * *

## Part 3: Exploratory data analysis

```{r}
## Subset The Movies 
names(movies)
desiredPredictors <- c("title_type","runtime","mpaa_rating","imdb_num_votes","critics_score","audience_score","genre","imdb_rating")

subsetMovies <-as.data.frame( movies[, desiredPredictors])
subsetMovies <- na.omit(subsetMovies)

head(subsetMovies)

# let's See Their Correlation for each numerical predictors
numericPredictors <- c("imdb_rating","runtime", "imdb_num_votes", "critics_score", "audience_score")

GGally::ggpairs(data = subsetMovies,columns = numericPredictors )



```


Seems Like Audience Score and Critics Score are highly correlated , m going to drop critics score since audience_Score is highly correlated with imdb_rating.

```{r}

# lets see the categorical variable then

str(subsetMovies) # We will fit it with all numerical data 

numericPredictors <- c("runtime", "imdb_num_votes", "critics_score", "audience_score")
categoricalPredictor <- c("title_type", "mpaa_rating", "genre")




index <- 1
ggplot_list <- list() # Creating Vector for keeping the plotted Objs
for (categoricalvarX in categoricalPredictor){
   if(categoricalvarX == "title_type"){
        print(categoricalvarX)
        FirstPlot <-   ggplot(data = subsetMovies,aes(y = imdb_rating,
                                                x = subsetMovies[, categoricalPredictor[1]]))+
                      ggplot2::geom_boxplot(aes(fill = subsetMovies[, categoricalPredictor[2]] ))+
                      ggplot2::labs(x = categoricalvarX )+
                      ggplot2::theme(axis.text.x = element_text(angle = 90)) + 
                      ggplot2::guides(fill = guide_legend(title = toupper(categoricalPredictor[2])))+
                      ggplot2::theme(legend.key.size = unit(0.5, "cm")) +
                      ggplot2::scale_y_continuous(limits = c(1, 10))
        
        SecondPlot <- ggplot(data = subsetMovies , aes(y = imdb_rating,
                                                       x = subsetMovies[, categoricalPredictor[1]]))+
                      ggplot2::geom_boxplot(aes(fill = subsetMovies[, categoricalPredictor[3]] ))+
                      ggplot2::labs(x = categoricalvarX) + 
                      ggplot2::theme(axis.text.x = element_text(angle = 90)) + 
                      ggplot2::guides(fill = guide_legend(title = toupper(categoricalPredictor[3])))+
                      ggplot2::theme(legend.key.size = unit(0.5, "cm"))+
                      ggplot2::scale_y_continuous(limits = c(1, 10))
                                 
        ggplot_list[[index]] <- FirstPlot
        ggplot_list[[index + 1]] <- SecondPlot
        print(index)
        index = index + 2
   }else if(categoricalvarX == "mpaa_rating"){
        print(categoricalvarX)   
        FirstPlot <-  ggplot(data = subsetMovies,aes(y = imdb_rating,
                                                x = subsetMovies[, categoricalPredictor[2]]))+
                      ggplot2::geom_boxplot(aes(fill = subsetMovies[, categoricalPredictor[1]] ))+
                      ggplot2::labs(x = categoricalvarX ) + 
                      ggplot2::theme(axis.text.x = element_text(angle = 90)) + 
                      ggplot2::guides(fill = guide_legend(title = toupper(categoricalPredictor[1])))+
                      ggplot2::theme(legend.key.size = unit(0.5, "cm"))+
                      ggplot2::scale_y_continuous(limits = c(1, 10))
        
        SecondPlot <- ggplot(data = subsetMovies , aes(y = imdb_rating,
                                                       x = subsetMovies[, categoricalPredictor[2]]))+
                      ggplot2::geom_boxplot(aes(fill = subsetMovies[, categoricalPredictor[3]] ))+
                      ggplot2::labs(x = categoricalvarX) +
                      ggplot2::theme(axis.text.x = element_text(angle = 90)) + 
                      ggplot2::guides(fill = guide_legend(title = toupper(categoricalPredictor[3])))+
                      ggplot2::theme(legend.key.size = unit(0.5, "cm"))+
                      ggplot2::scale_y_continuous(limits = c(1, 10))
                                 
        ggplot_list[[index]] <- FirstPlot
        ggplot_list[[index + 1]] <- SecondPlot   
        print(index)
        index = index + 2   
   }
    else if (categoricalvarX == "genre"){
        print(categoricalvarX)    
        FirstPlot <-  ggplot(data = subsetMovies,aes(y = imdb_rating,
                                                x = subsetMovies[, categoricalPredictor[3]]))+
                      ggplot2::geom_boxplot(aes(fill = subsetMovies[, categoricalPredictor[1]] ))+
                      ggplot2::labs(x = categoricalvarX )+
                      ggplot2::theme(axis.text.x = element_text(angle = 90)) + 
                      ggplot2::guides(fill = guide_legend(title = toupper(categoricalPredictor[1])))+
                      ggplot2::theme(legend.key.size = unit(0.5, "cm"))+
                      ggplot2::scale_y_continuous(limits = c(1, 10))
        
        SecondPlot <- ggplot(data = subsetMovies , aes(y = imdb_rating,
                                                       x = subsetMovies[, categoricalPredictor[3]]))+
                      ggplot2::geom_boxplot(aes(fill = subsetMovies[, categoricalPredictor[2]] ))+
                      ggplot2::labs(x = categoricalvarX)+
                      ggplot2::theme(axis.text.x = element_text(angle = 90)) + 
                      ggplot2::guides(fill = guide_legend(title = toupper(categoricalPredictor[2])))+
                      ggplot2::theme(legend.key.size = unit(0.5, "cm"))  +
                      ggplot2::scale_y_continuous(limits = c(1, 10))
        ggplot_list[[index]] <- FirstPlot
        ggplot_list[[index + 1]] <- SecondPlot   
        print(index)
        index = index + 2           
                
                
        }
}
?scale_y_continuous

plot(ggplot_list[[1]]) # Plot the x= title type by Mpaa_Rating

#plot(ggplot_list[[2]])

```
For documentary films , we see that imdb rating most likely have more variability at 70 to 80 + by all mpaa_rating

for feature films, wee see that IMDB rating most likely have more variability at5.5 to roughly around 70 and we have outliers for majority of mpaa_rating

For TV Movie films, we only have 2 MPAA_RATING only R and Unrated both have imdb score below 70 for R and below 60 most likely for Unrated


```{r}
plot(ggplot_list[[2]])
```
for Documentary we only have 3 genres ,2 genres have rating scores above 7 and 1 below 7, no outliers

for Feature film i guess the variability score is around 5 to 7.5 on average for all genres

for tv mvoie i guess we only have drama genre with majority have score 6.5 to 7.5 on average


```{r}

# Plot the x = mpaa_rating by title type and genre
plot(ggplot_list[[3]])

```
PG-13 "Parents Strongly Cautioned. Some Material May Be Inappropriate For Children Under 13."
PG: "Parental Guidance Suggested. Some Material May Not Be Suitable For Children."
G: "General Audiences-All Ages Admitted."
R: "Restricted, Under 17 Requires Accompanying Parent Or Adult Guardian."
NC-17: "No One 17 And Under Admitted."

for G , we have documentary and Feature Film with greatly variability score between 6 to around 7.5 

for Nc-17 we only have 1 type,feature film and the score variablity is around 6.5 to below 7.0

for pg we only have 2 types , 1 have higher score variability aka above 7.0 the documentary film and 1 below 7.0 the feature film.

for pg-13 we have highly score variability for the documentary type and also moderate score variability for feature film

for the R documentary seems have higher score variablity followed by tv mvoie and feature film on average


```{r}

plot(ggplot_list[[4]])

```
We can see here that genres is arbitary for PG-Pg13 and R  ,but heres the summary , im to lazy to write to conclusion ,sorry ..
```{r}
table(subsetMovies$genre,subsetMovies$mpaa_rating)

```

```{r}

plot(ggplot_list[[5]])

```

```{r}
plot(ggplot_list[[6]])


```
# Seems The chosen categorical variables the title type have a great score for predicting the imdb score, from the variability and Genres also the great one, since we always have documentary with highest score variability, probably because of the lack of dataset contain film about documentaries. I guess for this those 2 could be the best categorical variable compare with mpaa_rating .

* * *

## Part 4: Modeling

```{r}
names(subsetMovies)
modelLinRegression <- lm(formula = imdb_rating ~ runtime + imdb_num_votes + audience_score +
                                    genre  + title_type ,data = subsetMovies)
summary(modelLinRegression)

```
i m not going to really statistics when interpreting a slope , here's what i got,going to interpret the categorical not numeric because those obvious to interpret

so the base imdb score for all films/movies/documentaries , get 3.5 imdb score on average given all equal 0

if some movies/films/documentaries out and have the genre Documentary as an example, it would add score 2.6 on average for imdb score .
REMEMBER : you're trying to make story with data not show off your statistic skill , make yourself explanation ez to understand to majority of audience

lets try to know how much variability is explained by our model
```{r}
AnovaResultLinReg <- anova(modelLinRegression)
# 6 for residuals
paste("So Here's the percentage of the data that not explained by our model : ", sqrt(AnovaResultLinReg$`Sum Sq`[6]) ,"%" )

AnovaResultLinReg
# 
```
Not Bad For first attempt :D

Let's Diagnostics the Model

```{r}
# 1. Linear Relationship between predictors and y
TotalObservation <-1 : nrow(subsetMovies)

modelLinRegression$residuals
ggplot2::ggplot(data = modelLinRegression ,aes(x = TotalObservation ,y = .resid))+
  ggplot2::geom_point()+
  ggplot2::geom_hline(yintercept =  0 , col = "red" , linetype = "dashed")
plot(TotalObservation, modelLinRegression$residuals )

```
Seems yep most observation lies around 0 , which we can say this diagnostics is clear to go

Let's Check the normal Distribution of this guy residuals
```{r}
# 2. Nearly Normal residuals
histogram <- ggplot2::ggplot(data = modelLinRegression , aes(x = .resid))+
  ggplot2::geom_histogram(aes(y =..density..),fill= "orange",col = 'black',bins = 100) + 
  ggplot2::geom_density(col = "blue")
#qqplotplot <- 
ggplotQQ <- function(lm){
  # This Function Purpose
  # extract standardized residuals from the fit
  # and Create the qqplot with its line
    dfModel <- data.frame(std.resid = rstandard(model = lm))
    
    yAxis <- quantile(dfModel$std.resid,p = c(0.25,0.75))
    xAxis <- qnorm(p= c(0.25,0.75))
    slope <- diff(yAxis) / diff(xAxis)
    intercept <- yAxis[1] - slope * xAxis[1]
  
    plotted <- ggplot2::ggplot(data = dfModel, aes(sample = std.resid))  +stat_qq(shape = 1 ,size = 3)+
      geom_abline(slope = slope , intercept = intercept, linetype = "dashed",col= 'red') 
    return (plotted)
    
    
}
qqplotline <- ggplotQQ(modelLinRegression)

grid.arrange(histogram, qqplotline , nrow =1 ,ncol = 2 ,widths = c(4,2) )

```
below there it's because outliers but overall this is looks like normal shape :D

lets check constant variability
```{r}
ResidAndFittedPlt <- ggplot2::ggplot(data = modelLinRegression,aes(x = .fitted , y = .resid))+
  geom_point() +
  geom_hline(yintercept = 0, col = "red" , linetype ='dashed')

AbsResidAndFittedPlt <- ggplot2::ggplot(data = modelLinRegression,aes(x = .fitted , y = abs(.resid)))+
  geom_point() +
  geom_hline(yintercept = 0, col = "red" , linetype ='dashed')


grid.arrange(ResidAndFittedPlt , AbsResidAndFittedPlt , ncol = 2,nrow = 1 , widths = c(4,2))

```
I guess we can say this diagnostics is fine to , because fitted and resid most likely lies around 0 , remember this is lin reg, we have this result is a good enough , wecan improve it to , with polynomial model or doing randomforest

This is not time series , and the data collected randomly so we can assume that this data is independent residuals .


* * *

## Part 5: Prediction

```{r}
#lets try to see the predicted


pred.int <- predict(modelLinRegression , interval = "prediction")

ModifiedSubset <- cbind(subsetMovies[, c("title_type","runtime","imdb_num_votes", "audience_score", "genre", "imdb_rating")], pred.int)

head(ModifiedSubset)

```
# Well Not bad ,really not bad for this we not really far with the actual answer .

lets See the prediction and confidence interval thershold

```{r}
# just going to plot 1 of numerical variable
  ggplot2::ggplot(data = ModifiedSubset , aes(y = imdb_rating , x = fit))+
  geom_point()+
  geom_smooth( method = "lm" ) + 
  ggplot2::geom_line(aes(y = lwr),col = "red", linetype = "dashed")+
  ggplot2::geom_line(aes(y = upr),col = "red", linetype = "dashed")

```

* * *

## Part 6: Conclusion

So my conclusion,our Model is not bad at all ,we found that rouhgly 78 percent our model correctly predict given variables , and the prediction interval is quitely larger , and also we know that in this model we used only 7 variables and we come with a great r adjusted squared and loss the diagonostics test, so as far as i can tell the best predictors to predict this imdb_rating is : "title_type","runtime","imdb_num_votes" ,"audience_score", "genre" ,"imdb_rating" 

