---
title: "Statistical inference with the GSS data"
output: 'md_document'
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
setwd("D:/CourseraCourses/StatisticsWithR/Inference Statistics/Week5")
library(ggplot2)
library(dplyr)
library(statsr)
library(reshape2)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `gss`. Delete this note when before you submit 
your work. 

```{r load-data}
load("gss.Rdata")
```



* * *

## Part 1: Data

## Introduction

This extract of the General Social Survey (GSS) Cumulative File 1972-2012 provides a sample of selected indicators in the GSS.

Since 1972, the General Social Survey (GSS) has been monitoring societal change and studying the growing complexity of American society. 

Based on Information about gss i've read , turns out this data is a Sample from population.

```{r}
names(gss)
```

* * *

## Part 2: Research question

1. Are Race and religion of a Person tend to affecting his/her Suicide opinion ?  .

Reason : Based On https://www.macrotrends.net/countries/USA/united-states/suicide-rate
US Suicide Case kept raising , so i think it's a good idea to know exactly what they thinking about "Ending" his/her own life from race and religion perspective,in this scope.
* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note when before you submit your work.

```{r}
#Take Our Variables of interest

variables = c("race","relig","suicide1","suicide2","suicide3","suicide4")
subsetgss <- gss[,variables]

# Change the minor religions to Other
subsetgss$relig <- dplyr::if_else(subsetgss$relig == "Inter-Nondenominational" | subsetgss$relig =="Other Eastern" |  
                                subsetgss$relig == "Native American" , true = "Other" ,false = as.character(subsetgss$relig)) 

## Merge orthodox with Christian to one

subsetgss$relig <- dplyr::if_else(subsetgss$relig == "Orthodox-Christian" ,"Christian" , as.character(subsetgss$relig))

#Drop NA Values Since we want an answer for all .
subsetgss <- subsetgss[! is.na(subsetgss$relig) & ! is.na(subsetgss$suicide1) &
                       ! is.na(subsetgss$suicide2) & !is.na(subsetgss$suicide3) & ! is.na(subsetgss$suicide4),]
head(subsetgss)


## Turn Suicide Column into Var
subsetgssMelt <- reshape2::melt(data = subsetgss , id.vars = c("race","relig") , variable.name = "Suicidetype")
head(subsetgssMelt)
## Let's Check Race with 

ggplot2::ggplot(data = subsetgssMelt , aes(x = race,fill = Suicidetype))+
        ggplot2::geom_bar(position = "dodge") + 
        ggplot2::facet_grid(. ~ relig) + 
        ggplot2::theme(axis.text.x = element_text(angle = 90))
# Looks like Protestant and catholic are the majority answering this question followed by the Atheist / None.

```
```{r}
# Now Let's Focus On Protestant , catholic , None ,jewish and Other .

# we're going to drop Moslem , Buddhism , Hinduism , and Christian .

# Do you think a person has the right to end his or her own life if this person: a. Has an incurable disease?

Majority <- subset(subsetgss , relig == "Catholic" | relig == "Protestant" |
                           relig == "None" | relig == "Other" )
## Plot The suicide 1 Overall result

ggplot2::ggplot(data = Majority , aes(x = race , fill = suicide1)) + 
        ggplot2::geom_bar(position = "dodge") +
        ggplot2::facet_grid(. ~ c(relig)) +
        ggplot2::theme(axis.text.x = element_text(angle = 90)) 

## We can see Here , 3 out of 4 Religions are more likely to aggree with Questionare number 1

```
```{r}

## Let's See About second question 

# Do you think a person has the right to end his or her own life if this person: b. Has gone bankrupt?

ggplot2::ggplot(data = Majority , aes(x = race , fill = suicide2)) + 
        ggplot2::geom_bar(position = "dodge") +
        ggplot2::facet_grid(. ~ c(relig)) +
        ggplot2::theme(axis.text.x = element_text(angle = 90)) 

## Ah new intresting Cases : 

# We can see Here , 4 out of 4 Religions are more likely not to aggree with Question number 2


```
```{r}

# Let's See The Suicide 3  now

#Do you think a person has the right to end his or her own life if this person: c. Has dishonored his or her family?

ggplot2::ggplot(data = Majority , aes(x = race , fill = suicide3)) + 
        ggplot2::geom_bar(position = "dodge") +
        ggplot2::facet_grid(. ~ c(relig)) +
        ggplot2::theme(axis.text.x = element_text(angle = 90)) 


# Ah new intresting Cases : 

# We can see Here , 4 out of 4 Religions are more likely not to aggree with Question number 3


```

```{r}

# Letsee Last Question 

# Do you think a person has the right to end his or her own life if this person: d. Is tired of living and ready to die?

ggplot2::ggplot(data = Majority , aes(x = race , fill = suicide4)) + 
        ggplot2::geom_bar(position = "dodge") +
        ggplot2::facet_grid(. ~ c(relig)) +
        ggplot2::theme(axis.text.x = element_text(angle = 90)) 

# Ah new intresting Cases : 

# We can see Here , 4 out of 4 Religions are more likely not to aggree with Question number 3


```

* * *

## Part 4: Inference

### First Inference : 
```{r}
paste("We're going to inference the diffrent between the race and religion")

paste("H0 : There's no difference between race and religion")
paste("HA : There's a difference between race and religion")

paste("Checking Condition : ")
paste("Random Sampled , is achieved")
paste("Each case only contribute to one cell ,Achieved")
paste("Sample Size at least 5 cell achieved ")

paste("We're going to use Chi square test of difference")
paste("Using theoretical because our sample achived all assumptions")
paste("Using proportion ,because both is categorical variables")

statsr::inference(data = Majority ,y = race , x = relig ,method = "theoretical",
                  statistic = "proportion",type = "ht" ,null = 0 , alternative = "greater")
?inference

# From The output we know that we should Reject H0 , then our conclusion :
# There's a significance evidence that race and religion is difference  ie Dependent . 


```

```{r}
# Now lets see if yeses answers is dependent to religion and race . we'll take a look with religion first

paste("We're going to inference the diffrent between the race and religion")

paste("H0 : There's no difference between Suicide1 and religion")
paste("HA : There's a difference between Suicide1 and religion")

paste("Checking Condition : ")
paste("Random Sampled , is achieved")
paste("Each case only contribute to one cell ,Achieved")
paste("Sample Size at least 5 cell achieved ")

paste("We're going to use Chi square test of difference")
paste("Using theoretical because our sample achived all assumptions")
paste("Using proportion ,because both is categorical variables")

statsr::inference(data = Majority ,y = suicide1 , x = relig ,method = "theoretical",
                  statistic = "proportion",type = "ht" ,null = 0 ,
                  alternative = "greater",success = "yes")

## We Can See At our output , "yes" Answer in question 1 is Dependent with religion


```
```{r}

paste("We're going to inference the diffrent between the Suicide2 and religion")

paste("H0 : There's no difference between Suicide2 and religion")
paste("HA : There's a difference between Suicide2 and religion")

paste("Checking Condition : ")
paste("Random Sampled , is achieved")
paste("Each case only contribute to one cell ,Achieved")
paste("Sample Size at least 5 cell achieved ")

paste("We're going to use Chi square test of difference")
paste("Using theoretical because our sample achived all assumptions")
paste("Using proportion ,because both is categorical variables")

statsr::inference(data = Majority ,y = suicide2 , x = relig ,method = "theoretical",
                  statistic = "proportion",type = "ht" ,null = 0 ,
                  alternative = "greater",success = "no")

## We Can See At our output , "No" Answer in question 2 is Dependent with religion


```
```{r}
paste("We're going to inference the diffrent between the Suicide2 and religion")

paste("H0 : There's no difference between Suicide3 and religion")
paste("HA : There's a difference between Suicide3 and religion")

paste("Checking Condition : ")
paste("Random Sampled , is achieved")
paste("Each case only contribute to one cell ,Achieved")
paste("Sample Size at least 5 cell achieved ")

paste("We're going to use Chi square test of difference")
paste("Using theoretical because our sample achived all assumptions")
paste("Using proportion ,because both is categorical variables")

statsr::inference(data = Majority ,y = suicide3 , x = relig ,method = "theoretical",
                  statistic = "proportion",type = "ht" ,null = 0 ,
                  alternative = "greater",success = "no")

## We Can See At our output , "no" Answer in question 3 is also Dependent with religion


```

```{r}

paste("We're going to inference the diffrent between the Suicide4 and religion")

paste("H0 : There's no difference between Suicide4 and religion")
paste("HA : There's a difference between Suicide4 and religion")

paste("Checking Condition : ")
paste("Random Sampled , is achieved")
paste("Each case only contribute to one cell ,Achieved")
paste("Sample Size at least 5 cell achieved ")

paste("We're going to use Chi square test of difference")
paste("Using theoretical because our sample achived all assumptions")
paste("Using proportion ,because both is categorical variables")

statsr::inference(data = Majority ,y = suicide4 , x = relig ,method = "theoretical",
                  statistic = "proportion",type = "ht" ,null = 0 ,
                  alternative = "greater",success = "no")

## We Can See At our output , "no" Answer in question 4 is also Dependent with religion

```
```{r}

# Let's Check the Race now


paste("H0 : There's no difference between race and suicide1")
paste("HA : There's a difference between race and Suicide1")

paste("Checking Condition : ")
paste("Random Sampled , is achieved")
paste("Each case only contribute to one cell ,Achieved")
paste("Sample Size at least 5 cell achieved ")

paste("We're going to use Chi square test of difference")
paste("Using theoretical because our sample achived all assumptions")
paste("Using proportion ,because both is categorical variables")

statsr::inference(data = Majority ,y = suicide1 , x = race ,method = "theoretical",
                  statistic = "proportion",type = "ht" ,null = 0 ,
                  alternative = "greater",success = "yes")

## We Can See At our output , "yes" Answer in question 1 is also Dependent with race

```
```{r}


paste("H0 : There's no difference between race and suicide2")
paste("HA : There's a difference between race and Suicide2")

paste("Checking Condition : ")
paste("Random Sampled , is achieved")
paste("Each case only contribute to one cell ,Achieved")
paste("Sample Size at least 5 cell achieved ")

paste("We're going to use Chi square test of difference")
paste("Using theoretical because our sample achived all assumptions")
paste("Using proportion ,because both is categorical variables")

statsr::inference(data = Majority ,y = suicide2 , x = race ,method = "theoretical",
                  statistic = "proportion",type = "ht" ,null = 0 ,
                  alternative = "greater",success = "no")
## We Can See At our output , "no" Answer in question 2 is also Dependent with race

```
```{r}

paste("H0 : There's no difference between race and suicide3")
paste("HA : There's a difference between race and Suicide3")

paste("Checking Condition : ")
paste("Random Sampled , is achieved")
paste("Each case only contribute to one cell ,Achieved")
paste("Sample Size at least 5 cell achieved ")

paste("We're going to use Chi square test of difference")
paste("Using theoretical because our sample achived all assumptions")
paste("Using proportion ,because both is categorical variables")

statsr::inference(data = Majority ,y = suicide3 , x = race ,method = "theoretical",
                  statistic = "proportion",type = "ht" ,null = 0 ,
                  alternative = "greater",success = "no")

## We Can See At our output , "no" Answer in question 3 is also Dependent with race

```
```{r}

paste("H0 : There's no difference between race and suicide3")
paste("HA : There's a difference between race and Suicide3")

paste("Checking Condition : ")
paste("Random Sampled , is achieved")
paste("Each case only contribute to one cell ,Achieved")
paste("Sample Size at least 5 cell achieved ")

paste("We're going to use Chi square test of difference")
paste("Using theoretical because our sample achived all assumptions")
paste("Using proportion ,because both is categorical variables")

statsr::inference(data = Majority ,y = suicide4 , x = race ,method = "theoretical",
                  statistic = "proportion",type = "ht" ,null = 0 ,
                  alternative = "greater",success = "no")

## We Can See At our output , "no" Answer in question 3 is also Dependent with race

```
```{r}
# Interpretation :

paste("Now We Can Make an conclusion : people /opinion related to died ,more likely to say no and yes religion and race affected their answer, because we know that our life is simply once > whatever your struggle is kept fight it. Don't let your life go easily.But because we only used race and religion , there's might be another factor to affect someone suicide. ")

```


NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note when before you submit your work.